Deciding to Disclose

### 2015-06-22 Model.tex
Move payoff matrices back to main body

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}

>>>>

\begin{table}
\center
\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Non & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10 & 10 & 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2 & -1 & 10\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}

\caption{Payoff matrices\label{tab:Payoff-matrix}}
\end{table}

@@

In reality, learning is not exclusively from personal experience, and social learning plays an important role. In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
